Technical Report

### 2018-03-20 fully-abstract-comp/technical-report.tex
Fix code region definition.

\[
  \codereg{\ta,\overline{\sigma_{\mathrm{ret}}},\overline{\sigma_{\mathrm{clos}}},\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code,H^\mathrm{code}_\sigma \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code)
\]

\[
  H^\mathrm{code} \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code \; s \; \hat{W} = \left\{
    \npair{(\code,\code)} \mid
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand (\overline{\sigma_{\mathrm{ret}}} \cup \overline{\sigma_{\mathrm{clos}}}) = [\sigma_\baddr,\sigma_\eaddr] \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\[
  H^\mathrm{code}_\sigma \; \ta \; \overline{\sigma_{\mathrm{ret}}} \; \overline{\sigma_{\mathrm{clos}}} \; \code \; s \; \sigma \; \hat{W} = 
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \in \overline{\sigma_{\mathrm{ret}}}\tand\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \in \overline{\sigma_{\mathrm{ret}}}\tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma \in \overline{\sigma_{\mathrm{clos}}} \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\]

>>>>

\[
  \codereg{\ta,\sigma_\baddr,\nrcalls,\nrclosures,\code} \defeq (\pure,*,=,=,H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code,H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \nrclosures \; \code)
\]

\[
  H^\mathrm{code} \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \hat{W} = \left\{
    \npair{(\code,\code)} \mid
  \begin{multlined}
    \dom(\code) = [\aaddr,\baddr] \tand \sigma_\eaddr = \sigma_\baddr + \nrcalls+\nrclosures - 1 \tand \\
    \code(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr}
  \end{multlined}
  \right\}
\]
\lau{19-03-2018: Add the link capability to the above? code in ta?}
\begin{multline*}
  H^\mathrm{code}_\sigma \; \ta \; \sigma_\baddr \; \nrcalls \; \nrclosures \; \code \; s \; \sigma \; \hat{W} = \\
  \begin{array}[t]{l}
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrc(\rx,\lin,\baddr,\eaddr,\aaddr'+\calllen - 1),\\((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \aaddr = \aaddr' + \retoffset \tand \\
        \sigma = \sigma_\baddr + o \tand o < \nrcalls\\
        \lbrack \baddr, \eaddr \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus \\
\left\{
    \begin{array}{l}
\left. \npair{\arraycolsep=0pt\left(\array{l}\retptrd(\baddr,\eaddr),\\((\rw,\linear),\baddr,\eaddr,\aaddr)\endarray\right)} \middle| \right. \\
      \\
      \begin{array}{l}
        \exists r \in \dom(\pwpriv[\xi(\hat{W})]) \ldotp \pwpriv[\xi(\hat{W})](r) \nequal (\stareg[(\ms,\ms)]{\spa}, ((\rx,\lin),\baddr',\eaddr',\aaddr'+\calllen)) \tand \\
        \quad \dom(\ms) = [\baddr,\eaddr] \tand\\
        \quad \decInstr{\code([a',a' + \calllen-1])} = \overline{\scall{o}{r_1}{r_2}} \tand \\
        \quad \sigma = \sigma_\baddr + o \tand o < \nrcalls \tand\\
        \quad a = b-1\tand \\
        \quad \lbrack \baddr', \eaddr' \rbrack = \dom(\code) \subseteq \ta
      \end{array}
    \end{array}
      \right\} \uplus\\
    \left\{
    \begin{array}{l}
\left. \npair{(\vsc, \vsc' )} \middle| \right. \\
      \begin{array}{l}
        \sigma = \sigma_\baddr + o \tand \nrcalls \leq o < \nrcalls + \nrclosures \tand\\
        (\dom(\code) \mathrel{\#} \ta \tand \npair{\vsc,\vsc'} \in \lrv \; W) \tor\\
        (\dom(\code) \subseteq \ta)
      \end{array}
    \end{array}
      \right\}
  \end{array}
\end{multline*}
